LaMachine: A meta-distribution for NLP software

### 2019-01-16 docs/lamachine_clarin2018.tex
paper update

In addition, we have limited support for macOS (the local installation flavour) and the homebrew package
manager\footnote{Alternatives such as macports are not supported}, the support is limited because not all participating
software supports macOS.

@@

LaMachine also comes with  a
Jupyter Lab\footnote{\url{https://jupyter.org/}} environment which provides a web-based Integrated Development
Environment (IDE) for scripting in Python and R, web-based terminal access, and so-called \emph{notebooks} which mix
text, code and data output and have gained great popularity in data science community nowadays. This is shown in
Figure~\ref{fig:lab}.

>>>>

In addition, we have limited support for macOS (the local installation flavour), powered in part by the homebrew package
manager\footnote{Alternatives such as macports are not supported}. Support for macOS is limited because not all participating
software supports it.

@@

LaMachine also comes with a
Jupyter Lab\footnote{\url{https://jupyter.org/}} environment which provides a web-based Integrated Development
Environment (IDE) for scripting in Python and R, web-based terminal access, and so-called \emph{notebooks} which mix
text, code and data output and have gained great popularity in data science community. This is shown in
Figure~\ref{fig:lab}.
